D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling

### 2025-07-01 doc/article/article.tex
Updated paper

Some works in element recognition - like arrows - are particularly domain-specific (like medical imaging \cite{med1}\cite{med2}). Other studies focus on the so-called \textit{online recognition} task, whose goal is to recognize diagrams as they are drawn (see \cite{online1}, \cite{online2}, \cite{online3}). The online recognition task quite often employs the use of relative strokes, and is mainly focused on flowchart diagrams.

@@

	% Row 1
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{ex1.png}
		\caption{An easy flowchart diagram.}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=40pt, height=150pt]{ex2.png}
		\caption{The network's output.}
	\end{subfigure}

@@

	% Row 2
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{ex3.png}
		\caption{A complex graph diagram.}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=80pt, height=150pt]{ex4.png}
		\caption{The network's output.}
	\end{subfigure}

@@

	% Row 3
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{ex5.png}
		\caption{A complex flowchart diagram.}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{ex6.png}
		\caption{The network's output.}
	\end{subfigure}

@@

TODO: Nodo extra

>>>>

Some works in element recognition - like arrows - are particularly domain-specific (like medical imaging \cite{med1}\cite{med2}, or in circuit diagrams \cite{2024modular}). Other studies focus on the so-called \textit{online recognition} task, whose goal is to recognize diagrams as they are drawn (see \cite{online1}, \cite{online2}, \cite{online3} and especially \cite{framework} for a general framework). The online recognition task quite often employs the use of relative strokes, and is mainly focused on flowchart diagrams.

@@

	% Row 1
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{ex1.png}
		\caption{An easy flowchart diagram.}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=35pt, height=150pt]{ex2.png}
		\caption{The network's output.}
	\end{subfigure}

@@

	% Row 2
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{ex3.png}
		\caption{A complex graph diagram.}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=50pt, height=130pt]{ex4.png}
		\caption{The network's output.}
	\end{subfigure}

@@

	% Row 3
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\linewidth]{ex5.png}
		\caption{A complex flowchart diagram.}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=70pt, height=130pt]{ex6.png}
		\caption{The network's output.}
	\end{subfigure}

@@

We'd like to point out a few things about Figure~\ref{fig:results}. First of all, the result shown in part (d). A non-existing node can be seen in the upper right corner of the image; this is due to the fact that the self-arrow of node $q_5$ is recognized - by the object detection network - both as an arrow and as a node, with an high trust value. This problem could have been solved by applying a Non-Maxima Suppression - but in this specific case, the highest confidence value was surprisingly the node's one. This problem - that occasionally shows up - is probably to be attributed to the low samples present in the dataset.
